### 2014-09-04 doc/thesis/system.tex
Reviewing the typing rules of expressions

\begin{figure}[!ht]
\textbf{Type Language}\\
\dstart
$$
\begin{array}{rlr}
\multicolumn{3}{c}{\textbf{First-level types}}\\
T ::= & \;\; L & \textit{literal types}\\
& | \; B & \textit{base types}\\
& | \; \Nil & \textit{nil type}\\
& | \; \Value & \textit{top type}\\
& | \; \Any & \textit{dynamic type}\\
& | \; \Self & \textit{self type}\\
& | \; T \cup T & \textit{disjoint union types}\\
& | \; P \rightarrow R & \textit{function types}\\
& | \; \{ \}_{o|c} & \textit{empty table type}\\
& | \; \{F, ..., F\}_{o|c} & \textit{table types}\\
& | \; X & \textit{type variables}\\
& | \; \mu X.T & \textit{recursive types}\\
& | \; X_{i} & \textit{projection types}\\
L ::= & \False \; | \; \True \; | \; {\it number} \; | \; {\it string} & \\
B ::= & \Boolean \; | \; \Number \; | \; \String & \\
F ::= & K:T \; | \; \Const \; K:T & \textit{field types}\\ 
K ::= & L \; | \; B \; | \; \Value \; | \; \Any & \textit{key types}\\
\multicolumn{3}{c}{}\\
\multicolumn{3}{c}{\textbf{Second-level types}}\\
S ::= & \;\; T &\\
& | \; T* & \textit{vararg types}\\
& | \; T \times S & \textit{tuple types}\\
P ::= & \Void \; | \; S & \textit{parameters list type}\\
R ::= & \Void \; | \; S \; | \; S \cup R & \textit{return types}\\
\end{array}
$$
\dend
\caption{The abstract syntax of Typed Lua types}
\label{fig:typelang}
\end{figure}

@@

\begin{figure}[!ht]
\textbf{Abstract Syntax}\\
\dstart
$$
\begin{array}{rl}
s ::= & \;\; \mathbf{skip} \; | \;
s_{1} \; ; \; s_{2} \; | \;
\vec{l} = \vec{e}  \; | \;
\mathbf{while} \; e \; \mathbf{do} \; s \; | \;
\mathbf{if} \; e \; \mathbf{then} \; s_{1} \; \mathbf{else} \; s_{2}\\
& | \; \mathbf{local} \; \vec{n}{:}\vec{T} = \vec{e} \; \mathbf{in} \; s \; | \;
\mathbf{rec} \; n{:}T = f \; \mathbf{in} \; s \; | \;
\mathbf{return} \; \vec{e} \; | \;
a\\
e ::= & \;\; \mathbf{nil} \; | \;
\mathbf{false} \; | \;
\mathbf{true} \; | \;
{\it number} \; | \;
{\it string} \; | \;
{...} \; | \;
f \; | \;
\{ \; \vec{c}\; \} \\
& | \; e_{1} + e_{2} \; | \;
e_{1} \; {..} \; e_{2} \; | \;
e_{1} == e_{2} \; | \;
e_{1} < e_{2} \; | \;
e_{1} \; \mathbf{and} \; e_{2} \; | \;
e_{1} \; \mathbf{or} \; e_{2} \\
& | \; \mathbf{not} \; e \; | \;
- e \; | \;
\# \; e \; | \;
a \; | \;
l \; | \;
(e) \; | \;
{<}t{>} \; e\\
l ::= & \; n \; | \;
e_{1}[e_{2}]\\
a ::= & \;\; e_{1}(\vec{e_{2}}) \; | \;
e_{1}{:}n(\vec{e_{2}})\\
f ::= & \; \mathbf{fun} \; (){:}R \; s \; | \;
\mathbf{fun} \; ({...}{:}T){:}R \; s \; | \;
\mathbf{fun} \; (\vec{n}{:}\vec{T}){:}R \; s \; | \;
\mathbf{fun} \; (\vec{n}{:}\vec{T},{...}{:}T){:}R \; s\\
c ::= & \; [e_{1}] = e_{2}\\
n ::= & \; {\it name}\\
\end{array}
$$
\dend
\caption{Typed Lua abstract syntax}
\label{fig:syntax}
\end{figure}

>>>>

\begin{figure}[!ht]
\textbf{Type Language}\\
\dstart
$$
\begin{array}{rlr}
\multicolumn{3}{c}{\textbf{First-level types}}\\
T ::= & \;\; L & \textit{literal types}\\
& | \; B & \textit{base types}\\
& | \; \Nil & \textit{nil type}\\
& | \; \Value & \textit{top type}\\
& | \; \Any & \textit{dynamic type}\\
& | \; \Self & \textit{self type}\\
& | \; T \cup T & \textit{disjoint union types}\\
& | \; P \rightarrow R & \textit{function types}\\
& | \; \{ \}_{c|o|u} & \textit{empty table type}\\
& | \; \{F, ..., F\}_{c|o|u} & \textit{table types}\\
& | \; X & \textit{type variables}\\
& | \; \mu X.T & \textit{recursive types}\\
& | \; X_{i} & \textit{projection types}\\
L ::= & \False \; | \; \True \; | \; {\it number} \; | \; {\it string} & \\
B ::= & \Boolean \; | \; \Number \; | \; \String & \\
F ::= & K:T \; | \; \Const \; K:T & \textit{field types}\\ 
K ::= & L \; | \; B \; | \; \Value \; | \; \Any & \textit{key types}\\
\multicolumn{3}{c}{}\\
\multicolumn{3}{c}{\textbf{Second-level types}}\\
S ::= & \;\; T &\\
& | \; T* & \textit{vararg types}\\
& | \; T \times S & \textit{tuple types}\\
P ::= & \Void \; | \; S & \textit{parameters list type}\\
R ::= & \Void \; | \; S \; | \; S \cup R & \textit{return types}\\
\end{array}
$$
\dend
\caption{The abstract syntax of Typed Lua types}
\label{fig:typelang}
\end{figure}

@@

\begin{figure}[!ht]
\textbf{Abstract Syntax}\\
\dstart
$$
\begin{array}{rl}
s ::= & \;\; \mathbf{skip} \; | \;
s_{1} \; ; \; s_{2} \; | \;
\vec{l} = \vec{e}  \; | \;
\mathbf{while} \; e \; \mathbf{do} \; s \; | \;
\mathbf{if} \; e \; \mathbf{then} \; s_{1} \; \mathbf{else} \; s_{2}\\
& | \; \mathbf{local} \; \vec{n}{:}\vec{T} = \vec{e} \; \mathbf{in} \; s \; | \;
\mathbf{rec} \; n{:}T = f \; \mathbf{in} \; s \; | \;
\mathbf{return} \; \vec{e} \; | \;
a\\
e ::= & \;\; \mathbf{nil} \; | \;
\mathbf{false} \; | \;
\mathbf{true} \; | \;
{\it number} \; | \;
{\it string} \; | \;
{...} \; | \;
f \; | \;
\{ \; \vec{c} \; \} \\
& | \; e_{1} + e_{2} \; | \;
e_{1} \; {..} \; e_{2} \; | \;
e_{1} == e_{2} \; | \;
e_{1} < e_{2} \; | \;
e_{1} \; \mathbf{and} \; e_{2} \; | \;
e_{1} \; \mathbf{or} \; e_{2} \\
& | \; \mathbf{not} \; e \; | \;
- e \; | \;
\# \; e \; | \;
a \; | \;
l \; | \;
(e) \; | \;
{<}t{>} \; e\\
l ::= & \; n \; | \;
e_{1}[e_{2}]\\
a ::= & \; e_{1}(\vec{e_{2}}) \; | \;
e_{1}{:}n(\vec{e_{2}})\\
f ::= & \; \mathbf{fun} \; (){:}R \; s \; | \;
\mathbf{fun} \; ({...}{:}T){:}R \; s \; | \;
\mathbf{fun} \; (\vec{n}{:}\vec{T}){:}R \; s \; | \;
\mathbf{fun} \; (\vec{n}{:}\vec{T},{...}{:}T){:}R \; s\\
c ::= & \; [e_{1}] = e_{2}\\
n ::= & \; {\it name}\\
\end{array}
$$
\dend
\caption{Typed Lua abstract syntax}
\label{fig:syntax}
\end{figure}
